The SCOC acknowledges significant efforts and expresses immense gratitute to many dedicated members of the Rubin LSST Science Collaborations and broader scientific community who contributed to the optimization of the Rubin LSST Survey Strategy for many years and continue to actively engage with the SCOC on this topic. 

The SCOC is grateful to the Survey Strategy team who supported the SCOC work and the community contribution to the optimization of the Rubin LSST survey strategy: 
Dr. Peter Yoachim, 
Dr. Eric Neilson,
Dr. Tiago Ribeiro, and Dr. Lynne Jones.

Rubin Observatory Construction Project and Operations acknowledge and thank the SCOC members for their significant and sustained   work toward the design of the LSST observing strategy and in particular express their gratitude to the outgoing members of the committee: Dr. Sarah Brough, Dr. Renée Hložek, Dr. Mansi Kasliwal, Dr. Hiranya Peiris, Dr. Meg Schwamb, Dr. Dan Scolnic.

\subsection{SCOC membership}

During the Phase 2 deliberations, the SCOC composition was as follows:

 Franz Bauer, Universidad Católica, Chile

 Federica Bianco, Rubin Observatory/University of Delaware (ex officio, chair)

 Sarah Brough, University of New South Wales 

 Renee Hlozek, University of Toronto


 Lynne Jones, Rubin Observatory (ex officio)

 Mansi Kasliwal, Caltech 

 Knut Olsen, NSF’s NOIRLab 

 Hiranya Peiris, University College London/Stockholm University

 Meg Schwamb, Queen's University Belfast

 Dan Scolnic, Duke University

 Colin Slater, University of Washington  

 Jay Strader, Michigan State University

